### 2015-04-16 README.Rmd
Testing superscript

Thomas E. White1, Rhiannon L. Dalrymple2, Daniel W. A. Noble1,2, James C. O’Hanlon 1, Daniel B. Zurek3, Kate D. L. Umbers4,5,6

@@

### Introduction
This repository contains data collected from the literature to assess to quality of reporting in signal-based colour studies of animal and plant taxa. Our literature search includes studies collected in 2013 from research journals likley to do colour signal research. We also detail important methodological deatils that ideally should be reported in studies that quantify colour using both spectrophotometry and camera equipment along with important analytical parameters used for visual modelling.

>>>>

Thomas E. White<sup>1</sup>, Rhiannon L. Dalrymple2, Daniel W. A. Noble1,2, James C. O’Hanlon 1, Daniel B. Zurek3, Kate D. L. Umbers4,5,6

@@

### Introduction
This repository contains data collected from the literature to assess to quality of reporting in signal-based colour studies of animal and plant taxa. Our literature search includes studies collected in 2013 from research journals likley to do colour signal research. We also detail important methodological details that ideally should be reported in studies that quantify colour using both spectrophotometry and camera equipment along with important analytical parameters used for visual modelling.
